Would NEMO benefit from using the \psyclone\ system?

### 2015-11-20 docs/NEMO/psyclone_and_nemo.tex
NEMO: add discussion of example code provided by Rupert

\subsection{An example: ldf\_slp\_triad}

Rupert mocking this up.

>>>>

\subsection{An example: ldf\_slp}

As an example, we have manually re-structured the {\it ldf\_slp}
routine following the \psykal\ separation of concerns. The resulting
code is too long to include here but may be obtained from the GOcean
SVN repository on puma:
\begin{verbatim}
> svn list https://puma.nerc.ac.uk/svn/GOcean_svn/GOcean/trunk/\
docs/NEMO/example
horizontal_density_gradient_u_mod.f90
horizontal_density_gradient_v_mod.f90
ldf_slp_alg.f90
ldf_slp_alg_processed.f90
ldfslp.F90
psy.f90
\end{verbatim}

Here, ldfslp.F90 is the original routine, ldf\_slp\_alg.f90 is the
Algorithm layer, psy.f90 contains the (manually written) PSy layer and
the horizontal\_density\_$\ast$.f90 files contain kernels.
ldf\_slp\_alg\_processed.f90 contains the Algorithm layer as it would
appear after processing by \psyclone.
